Appendix 1: sdmTMB statistical model description

### 2021-12-21 doc/appendix-model.Rmd
Add refs

[Source code](https://kaskr.github.io/adcomp/tweedie_8cpp_source.html) as in the [cplm](https://CRAN.R-project.org/package=cplm) package [@zhang2013a].

@@

@@

TMB allows for anisotropy, where spatial covariance may be asymmetric with respect to latitude and longitude ([full details](https://kaskr.github.io/adcomp/namespaceR__inla.html)). Anisotropy can be turned on and off with the logical `anisotropy` argument to `sdmTMB()`. There are a number of ways to implement anisotropic covariance REF, and we adopt a 2-parameter rotation matrix $\textbf{H}$. The elements of $\textbf{H}$ are defined by the parameter vector $\textbf{x}$ so that $H_{1,1} = x_{1}$, $H_{1,2} = H_{2,1} = x_{2}$ and $H_{2,2} = (1 + x_{2}^2) / x_{1}$

>>>>

@@

The [source code](https://kaskr.github.io/adcomp/tweedie_8cpp_source.html) is implemented as in the [cplm](https://CRAN.R-project.org/package=cplm) package [@zhang2013a] and is based on @dunn2005.

@@

TMB allows for anisotropy, where spatial covariance may be asymmetric with respect to latitude and longitude ([full details](https://kaskr.github.io/adcomp/namespaceR__inla.html)). Anisotropy can be turned on and off with the logical `anisotropy` argument to `sdmTMB()`. There are a number of ways to implement anisotropic covariance [@fuglstad2015a], and we adopt a 2-parameter rotation matrix $\textbf{H}$. The elements of $\textbf{H}$ are defined by the parameter vector $\textbf{x}$ so that $H_{1,1} = x_{1}$, $H_{1,2} = H_{2,1} = x_{2}$ and $H_{2,2} = (1 + x_{2}^2) / x_{1}$.
